Exposure Consequences - Statistics and Figures

### 2018-02-07 ManuscriptMaterials.Rmd
fixed peaks for localization

```{r localization_peaks}
getPeakLocConfidenceInterval(group='classic',CIs=c(.95), movementtype='both', LRpart='all')
getPeakLocConfidenceInterval(group='exposure',CIs=c(.95), movementtype='both', LRpart='all')
```

These results are strange: the median peak for the exposure localization is around 42 degrees. If we look at the plot, it is much higher though, somewhere between 55 and 65 probably. This doesn't change much if I only look at the passive or at the active localization data. The peak for classic makes sense though.

@@

```{r}
for (name in names(correlations)) {
  cat(name)
  print(correlations[[name]][['cortest']])
}
```

@@

```{r eval=FALSE, include=FALSE}
# this code won't run or show up in output, just included here if you want to play with it:
for (name in names(correlations)) {
  cat(name)
  print(correlations[[name]][['linearm']])
}
```

@@

```{r}
multipleRegressionLocalization(group='exposure',NCpart='initial')
```

@@

```{r}
multipleRegressionLocalization(group='classic',NCpart='initial')
```

@@

```{r}
# THIS FAILS NOW... maybe because some participants don't have data in the first half?
multipleRegressionLocalization(group='exposure',NCpart='initial', LRpart='first')
```

@@

```{r}
multipleRegressionLocalization(group='online',NCpart='initial')
```

>>>>

```{r localization_peaks}
getPeakLocConfidenceInterval(group='classic',CIs=c(.95), movementtype='active', LRpart='all')
getPeakLocConfidenceInterval(group='exposure',CIs=c(.95), movementtype='active', LRpart='all')
```

These results mimic those of the reach aftereffects: the median values are different, but they each fall in the other confidence interval. If we want to look at this better, we need to get better estimates of these curves in every participants, by having a wider range of points and more data per point, but probably also larger rotations.

@@

```{r pearson_rhos}
for (name in names(correlations)) {
  cat(name)
  print(correlations[[name]][['cortest']])
}
```

@@

```{r linreg, eval=FALSE, include=FALSE}
# this code won't run or show up in output, just included here if you want to play with it:
for (name in names(correlations)) {
  cat(name)
  print(correlations[[name]][['linearm']])
}
```

@@

```{r step_exposure}
multipleRegressionLocalization(group='exposure',NCpart='initial')
```

@@

```{r step_classic}
multipleRegressionLocalization(group='classic',NCpart='initial')
```

@@

```{r step_exposure_firsthalf}
multipleRegressionLocalization(group='exposure',NCpart='initial', LRpart='first')
```

@@

```{r step_online}
multipleRegressionLocalization(group='online',NCpart='initial')
```
